---
title: "I am a bot and so can you!"
author: "Dillon Niederhut & Juan Shishido"
date: "March 6, 2015"
output: ioslides_presentation
---

# Introduction to your robot overlords

## What is a bot?

## Who wants a bot?

## What would you do with a bot?

# Introduction to Twitter

## What's in a tweet?

## How to set up your authentication

## What's an API?

## What can I as Twitter?

## What will Twitter give me?

# Introduction to Python

## What is requests?

## What is a boilerplate?

## How do I make it work?

## How do I make it my own?



# Juan - the stuff below is some example formatting that RStudio gives you whenever you make one of these files in their GUI. To see more about how Rmd renders into HTML slides, you check out my github repo at deniederhut/workshop_Rmd

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

